SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars

### 2015-09-07 papers/B1555_EdgeOn/B1555_letter.tex
update for Matt's comment
changes in modelling about starting point setting

To obtain the best-fit lens model, we explore the parameter space with the following steps. First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$  for the exponential disc. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile. The rest of the parameters that describe the exponential disc are set to be the same as the SIE component as the starting point. All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec). The total number of free parameters is 13. After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.

>>>>

To obtain the best-fit lens model, we explore the parameter space with the following steps. First, to pick up a set of starting parameters, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles. However, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$ for the exponential disc. All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec). The total number of free parameters is 13. After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.
